Characterizing Signal Loss, Error, and Bias in the 21cm Reionization \\Power Spectrum: A Revised Study of PAPER-64

### 2018-01-26 PAPER.tex
added switzer recommended refs

Driven by the need to mitigate foreground bias, PAPER's previous analyses use a weighting method that aims to down-weight 
foregrounds. This weighting is applied to data, which is then propagated into a final estimator using the power spectrum 
estimation technique of optimal quadratic estimators (OQE) as done in \citet{liu_tegmark2011}, \citet{dillon_et_al2013a}, \citet{liu_et_al2014a}, \citet{liu_et_al2014b}, \citet{trott_et_al2012}, \citet{dillon_et_al2014}, \citet{dillon_et_al2015}, and \citet{trott_et_al2016}. Before showing 
how signal loss can arise when using different weighting matrices, we first summarize OQE as performed in the PAPER 
analysis.

@@

Without a perfect model for the covariance matrix $\textbf{C}$ of our data, one attractive way to estimate it is to empirically derive it from the data $\textbf{x}$ itself (this is what was done in the previous PAPER analyses). For instance, one could time-average such that:

@@

In Section \ref{sec:SiglossOverview}, we showed how signal loss arises when weighting data using information from the data 
itself. Here we describe a methodology for estimating the amount of signal loss caused by a particular power spectrum estimator when applied to a particular data set. The exact signal loss ``correction factor" for a particular data set will depend on the specific realizations of the signals present in the data and is not something we can directly compute. 
In this work, we inject simulated cosmological signals into our data and test the recovery of those signals in order to statistically quantify 
the amount of signal loss accompanying a weighting scheme used in OQE power spectrum estimation.  
There are, in fact, several different ways of incorporating the result of such a calculation into a revised power spectrum estimate which accounts for signal loss.  In this section, we describe a methodology for determining an approximate correction factor which can be applied to a power spectrum estimate; in Appendix \ref{sec:Pr_appendix}, we present an alternate framework that explicitly interprets all measurements as upper limits in the presence of signal loss.  
These two methods yield very similar results, but fundamentally are answering subtly distinct questions.  
We also highlight major differences from the signal loss 
computation used in A15, which previously underestimated losses.

@@

The correlation between $\widehat{\textbf{C}}_r^{-1}\textbf{e}$ and $\widehat{\textbf{C}}_r^{-1}\textbf{x}$ means that we cannot compute signal loss using a signal-only 
simulation, which would yield greater values for $P_{\rm out}$ and thereby underestimate signal loss. Therefore, in our revised 
signal loss computation we use the full quantity for $P_{\rm out}$ as defined in Equation \eqref{eq:sigloss}, which subtracts the 
weighted power spectrum of the data from the weighted power spectrum of data plus EoR.

@@

We saw in Section \ref{sec:otherweight} how limiting the number of down-weighted eigenmodes (i.e. flattening out part of the 
eigenspectrum and effectively de-coupling the `weak' eigenmodes from the data) can help minimize signal loss. We experiment with this idea on PAPER-64 data, dialing the number of modes 
that are down-weighted from zero (which is equivalent to identity-weighting, or the unweighted case) to $21$ (which is full inverse 
covariance weighting of our $21$ channels). The power spectrum results for one $k$ value, both before and after signal loss 
estimation, are shown in the top panel in Figure \ref{fig:sigloss_modeloop}. We see that the amount of signal loss increases as weighting 
becomes more aggressive (gray curve). In other words, more `weak' (EoR-dominated) fluctuations are being overfit and 
subtracted as more modes are down-weighted. We also find that the power spectrum upper limit, post signal loss estimation, 
increases with the number of down-weighted modes (black curve). The more modes we use in down-weighting, the stronger the coupling between the weighting and the data, and the greater the error we have in estimating the power spectrum.

>>>>

Driven by the need to mitigate foreground bias, PAPER's previous analyses use a weighting method that aims to down-weight 
foregrounds. This weighting is applied to data, which is then propagated into a final estimator using the power spectrum 
estimation technique of optimal quadratic estimators (OQE) as done in \citet{liu_tegmark2011}, \citet{dillon_et_al2013a}, \citet{liu_et_al2014a}, \citet{liu_et_al2014b}, \citet{trott_et_al2012}, \citet{dillon_et_al2014}, \citet{dillon_et_al2015}, \citet{switzer_et_al2015}, and \citet{trott_et_al2016}. Before showing 
how signal loss can arise when using different weighting matrices, we first summarize OQE as performed in the PAPER 
analysis.

@@

Without a perfect model for the covariance matrix $\textbf{C}$ of our data, one attractive way to estimate it is to empirically derive it from the data $\textbf{x}$ itself. Similar types of weightings that are based on variance information in data are done in \citet{chang_et_al2010} and \citet{switzer_et_al2015}. In previous PAPER analyses, one time-averages the data such that:

@@

In Section \ref{sec:SiglossOverview}, we showed how signal loss arises when weighting data using information from the data 
itself. Here we describe a methodology for estimating the amount of signal loss caused by a particular power spectrum estimator when applied to a particular data set. The exact signal loss ``correction factor" for a particular data set will depend on the specific realizations of the signals present in the data and is not something we can directly compute. 
In this work, we inject simulated cosmological signals into our data and test the recovery of those signals in order to statistically quantify 
the amount of signal loss accompanying a weighting scheme used in OQE power spectrum estimation (an approach also taken by \citet{masui_et_al2013}).  
There are, in fact, several different ways of incorporating the result of such a calculation into a revised power spectrum estimate which accounts for signal loss.  In this section, we describe a methodology for determining an approximate correction factor which can be applied to a power spectrum estimate; in Appendix \ref{sec:Pr_appendix}, we present an alternate framework that explicitly interprets all measurements as upper limits in the presence of signal loss.  
These two methods yield very similar results, but fundamentally are answering subtly distinct questions.  
We also highlight major differences from the signal loss 
computation used in A15, which previously underestimated losses.

@@

The correlation between $\widehat{\textbf{C}}_r^{-1}\textbf{e}$ and $\widehat{\textbf{C}}_r^{-1}\textbf{x}$ means that we cannot compute signal loss using a signal-only 
simulation, which would yield greater values for $P_{\rm out}$ and thereby underestimate signal loss. This argument is also made in \citet{switzer_et_al2015} in regards to estimating loss associated with foreground cleaning of GBT data. Therefore, in our revised 
signal loss computation we use the full quantity for $P_{\rm out}$ as defined in Equation \eqref{eq:sigloss}, which subtracts the 
weighted power spectrum of the data from the weighted power spectrum of data plus EoR.

@@

We saw in Section \ref{sec:otherweight} how limiting the number of down-weighted eigenmodes (i.e. flattening out part of the 
eigenspectrum and effectively de-coupling the `weak' eigenmodes from the data) can help minimize signal loss. We experiment with this idea on PAPER-64 data, dialing the number of modes 
that are down-weighted from zero (which is equivalent to identity-weighting, or the unweighted case) to $21$ (which is full inverse 
covariance weighting of our $21$ channels). The power spectrum results for one $k$ value, both before and after signal loss 
estimation, are shown in the top panel in Figure \ref{fig:sigloss_modeloop}. We see that the amount of signal loss increases as weighting 
becomes more aggressive (gray curve). In other words, more `weak' (EoR-dominated) fluctuations are being overfit and 
subtracted as more modes are down-weighted. We also find that the power spectrum upper limit, post signal loss estimation, 
increases with the number of down-weighted modes (black curve). The more modes we use in down-weighting, the stronger the coupling between the weighting and the data, and the greater the error we have in estimating the power spectrum. \citet{switzer_et_al2013} took a similar approach in determining the optimal number of modes to down-weight in GBT data, finding similar trends and noting that removing too few modes is limited by residual foregrounds and removing too many modes is limited by large error bars and signal loss.
